\bf Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid

### 2014-09-17 Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid/main.tex
Misedd this commit.

Equation~\ref{eq-hboa-stop} can also be simplified when doing comparisons. If model $B'$ has exactly one more
leaf than model $B$ than $p(B)$ and $p(B')$ the ratio $\frac{p(B)}{p(B')}$ simplifies to $2^{0.5 log_2\mu}$ regardless of
total model size.

>>>>

Equation~\ref{eq-hboa-stop} can also be simplified when doing comparisons. If model $B'$ has exactly one more
leaf than model $B$ than the ratio $\frac{p(B)}{p(B')}$ simplifies to $2^{0.5 log_2\mu}$ regardless of
total model size.
